Characterize the fetal kidney reference from the kidney cell atlas

### 2024-11-15 analyses/cell-type-wilms-tumor-06/notebook_template/00b_characterize_fetal_kidney_reference_Stewart.Rmd
fix typos in 00b and 02b, and re-render 00b

The aim is to characterize the human fetal kidney from the kidney cell atlas.
You can find more about the human kidney atlas here: https://www.kidneycellatlas.org/ [1]
The rds data can be download using the download link https://datasets.cellxgene.cziscience.com/40ebb8e4-1a25-4a33-b8ff-02d1156e4e9b.rds
The reference was downloaded and created in the script `scripts/prepare-fetal-references.R`.

@@

The input file `r params$fetal_kidney_path` is the output of the `R script` `prepare-fetal-references.R`.

@@

We will save the result of the differential expression analysis in results/references/00b_marker_genes_fetal_kidney_Stewart.csv
Notebook is saved in the `notebook/00-reference` directory

@@

We run DElegate::FindAllMarkers2 to find markers of the different clusters and manually check if they do make sense. 
DElegate::FindAllMarkers2 is an improved version of Seurat::FindAllMarkers based on pseudobulk differential expression method. 
Please check the preprint from Chistoph Hafemeister: https://www.biorxiv.org/content/10.1101/2023.03.28.534443v1
and tool described here: https://github.com/cancerbits/DElegate

>>>>

The aim is to characterize the human fetal kidney from the kidney cell atlas.
You can find more about the human kidney atlas here: https://www.kidneycellatlas.org/ [1]
The rds data can be download using the download link: <https://datasets.cellxgene.cziscience.com/40ebb8e4-1a25-4a33-b8ff-02d1156e4e9b.rds>.
The reference was downloaded and created in the script `scripts/prepare-fetal-references.R`.

@@

The input file `r params$fetal_kidney_path` is the output of the script `prepare-fetal-references.R`.

@@

We will save the result of the differential expression analysis in `results/references/00b_marker_genes_fetal_kidney_Stewart.csv`.
Notebook is saved in the `notebook/00-reference` directory.

@@

We run `DElegate::FindAllMarkers2()` to find markers of the different clusters and manually check if they do make sense. 
`DElegate::FindAllMarkers2()` is an improved version of `Seurat::FindAllMarkers()` based on pseudobulk differential expression method. 
Please check the preprint from Hafemeister and Halbritter: https://www.biorxiv.org/content/10.1101/2023.03.28.534443v2
and tool described here: https://github.com/cancerbits/DElegate
